---
title: "p8105_hw1_fz2328"
author: "Fengdi Zhang"
date: "2022-09-22"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
```

## Problem 1

Loading Dataset: The `penguins` dataset would be used for analysis in this homework.

```{r}
data("penguins", package = "palmerpenguins")
```

This dataset has `r nrow(penguins)` rows and `r ncol(penguins)` columns. 
It includes `r nrow(penguins)` penguin observations and describes their species, habitation islands, and biological characteristics, such as flipper lengths, body mass, sex and year. 
Their flipper length mean is `r round(mean(penguins$flipper_length_mm, na.rm = TRUE),2)` mm, and the bill length mean is `r round(mean(penguins$bill_length_mm, na.rm = TRUE),2)` mm. 

Below is an overview of the first 10 rows of the `penguins` dataset that we just loaded:

```{r, echo=FALSE}
head(penguins, 10)
```

Here we also have a summary for the `r ncol(penguins)` variables in this dataset:

```{r, echo=FALSE}
summary(penguins)
```

We also made a scatterplot of their flipper length and bill length.

```{r, echo=FALSE}
(ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) 
+ geom_point(na.rm = TRUE))
```


## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
