---
title: "p8105_hw1_fz2328"
author: "Fengdi Zhang"
date: "2022-09-22"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
```

## Problem 1

Loading Dataset: The `penguins` dataset would be used for analysis in this homework.

```{r}
data("penguins", package = "palmerpenguins")
```

This dataset has `r nrow(penguins)` rows and `r ncol(penguins)` columns. 
It includes `r nrow(penguins)` penguin observations and describes their species, habitation islands, and biological characteristics, such as flipper lengths, body mass, sex and year. 
Their flipper length mean is `r round(mean(penguins$flipper_length_mm, na.rm = TRUE),2)` mm, and the bill length mean is `r round(mean(penguins$bill_length_mm, na.rm = TRUE),2)` mm. 

Below is an overview of the first 10 rows of the `penguins` dataset that we just loaded:

```{r, echo=FALSE}
head(penguins, 10)
```

Here we also have a summary for the `r ncol(penguins)` variables in this dataset:

```{r, echo=FALSE}
summary(penguins)
```

We also made a scatterplot of their flipper length and bill length.

```{r, echo=FALSE}
(ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) 
+ geom_point(na.rm = TRUE))
```


## Problem 2

* First, we would use the following code to create a data frame named `Problem_2`comprised of:
    + a random sample of size 10 from a standard Normal distribution
    + a logical vector indicating whether elements of the sample are greater than 0
    + a character vector of length 10
    + a factor vector of length 10, with 3 different factor “levels”

```{r}
Problem_2 = tibble(
                    random_sample = rnorm(10),
                    vec_log = random_sample > 0,
                    vec_char = "abc",
                    vec_factor = factor(c("a", "b", "c","a", "b", "c","a", "b", "c","a" )))
```




Now, try to take the mean of the four variables in `Problem_2` using the following code, and outputs are also included:
```{r}
mean(pull(Problem_2, var = random_sample))
mean(pull(Problem_2, var = vec_log))
mean(pull(Problem_2, var = vec_char))
mean(pull(Problem_2, var = vec_factor))

```

The mean values were returned for the variables `random_sample` and `vec_log` as `r mean(pull(Problem_2, var = random_sample))` and `r mean(pull(Problem_2, var = vec_log))`, respectively. However, the mean function did not work for the variables `var_char` and `var_factor`and returned `NA`. 


Then, Let's try to apply the `as.numeric` function to the logical, character and factor variables:
```{r, warning=FALSE, results='hide'}
Problem_2$vec_log = as.numeric(pull(Problem_2, var = vec_log)) 
Problem_2$vec_char = as.numeric(pull(Problem_2, var = vec_char)) 
Problem_2$vec_factor = as.numeric(pull(Problem_2, var = vec_factor))
```
We can see that numerical values are assigned to the logical vector and the factor vector, but `NAs` are assigned to the character vector. 

Now, let's try to take the mean for the logical, character and factor variables again

```{r}
mean(pull(Problem_2, var = vec_log))
mean(pull(Problem_2, var = vec_char))
mean(pull(Problem_2, var = vec_factor))
```

We can see that a same mean value of  `r mean(pull(Problem_2, var = vec_log))` is returned for the logical vector as it was before applying the `as.numeric` function. A `NA` is still returned for the character vector, which is also the same as before. However, it is different for the factor variable `vec_factor` that a mean value of `r mean(pull(Problem_2, var = vec_factor))` is returned after the applying the `as.numeric` function.

This is because the logical variable has always been treated as a numeric vector with 2 values. The factor variable has 3 level, so it could be treated as numbers as well after applying the `as.numeric` function. However, there is no way to convert the character variable to numeric, so mean value could not be calculated for it all the time. This also reflects that mean values could only be taken for those variables which could be treated as numeric variables. 